---
title: "Module11_Homework"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework 10

**In this homework, you need to create two working functions that will help you with your data analysis.**  

### Solution

#### 1. Find Path Function

```{r, eval=FALSE}
findPathFunction.N <- function(startStation, endStation) {
    path <- startStation
    
    while(startStation != endStation) {
        for (i in 1:nrow(stations.N))
        {
            if(startStation == stations.N$stationid[i] ) {
                
                startStation <- stations.N$downstream[i]
                path <- rbind(path, stations.N$downstream[i])
                
                if(stations.N$downstream[i] == 0) {	
                	break	
                } 
            } 
        } 
    }			
    return(path)
}
```

 This function is used to find a path between two stations in __North__ direction.\  
 You just need to get two stations from _stations.N_ dataset and then call the function with these two station Ids. 
 
 **Example:**  _findPathFunction.N(1045,1140)_  
 
 
 

#### 2. Generate a Speed List for Loop 1350
```{r, eval=FALSE}
speedFunc <- function(na.rm = FALSE) {
	speedList <- 0
	for (i in 1:nrow(loop.1350)) {
		
		if (na.rm == TRUE) {
			if(!is.na(loop.1350$speed[i])){
				speedList <- rbind(speedList, loop.1350$speed[i])
			}
		} else {
			speedList <- rbind(speedList, loop.1350$speed[i])
		}	
	}
	return(speedList)
}

```


 This function is used to get a speed list for data in _loop.1350_ dataset.  
 
 **Function call:**  _speedFunc(na.rm=TRUE)_  

